The pollination trade-off

### 2019-05-07 paper/supp-info.Rmd
Change aspect ratio of heterospecific vs conspecific pollen figure

```{r fig-conspecififc-heterospecific, fig.height=2, fig.width = 3.57, fig.cap="Despite the variation in these slopes, plants overall had more conspecific than heterospecific pollen deposited in their stigmas."}
# fig_hetero_con <- make_fig_con_hetero_empirical(dep_frame)
drake::loadd(fig_hetero_con)
fig_hetero_con
```

>>>>

```{r fig-conspecififc-heterospecific, fig.height=4, fig.cap="Despite the variation in these slopes, plants overall had more conspecific than heterospecific pollen deposited in their stigmas."}
# fig_hetero_con <- make_fig_con_hetero_empirical(dep_frame)
drake::loadd(fig_hetero_con)
fig_hetero_con 
```
